---
title: "Activity_Code"
date: "8/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hello! In this markdown, we're going to play with the activity data. Let's jump right in.

First, let's load some packages
```{r}
#Activity levels

#First, let's load some packages
library(ggplot2)
library(glmmTMB)
library(gridExtra)
library(tidyr)
library(dplyr)
library(AICcmodavg)

#for kind of cool output tables
library(sjPlot)
library(DHARMa)
library(insight)

```
Let's load some data!

These files are divided into preactivity (10 minute period post-acclimation) and post activity (60 minute experiment)

```{r}
pre_activity_sums<- read.csv("pre_activity_sums.csv", header = T, sep = ",")
post_activity_sums<- read.csv("post_activity_sums.csv", header = T, sep = ",")

#Releveling the data
#Relevel----
levels(pre_activity_sums$Relatedness)
pre_activity_sums$Relatedness<- factor(pre_activity_sums$Relatedness, levels = c("Nonsibs", "Halfsibs", "Sibs"))

levels(pre_activity_sums$Size)
pre_activity_sums$Size<- relevel(pre_activity_sums$Size, "Small")

levels(post_activity_sums$Relatedness)
post_activity_sums$Relatedness<- factor(post_activity_sums$Relatedness, levels = c("Nonsibs", "Halfsibs", "Sibs"))
post_activity_sums$Size<- relevel(post_activity_sums$Size, "Small")
```

#GRAPHICAL EXPLORATION
Now that we've got out data all tidyed up, let's go ahead and look at that sweet sweet ggplot style. I'm thinking boxplots are the way to go here. 

```{r}
#Pre Activity

ggplot(pre_activity_sums, aes( x = Relatedness, y = Swim, color = Size)) + 
  geom_boxplot()+
  geom_point(position=position_jitterdodge(), alpha = 0.3)+
  ylab("Acclimation Swimming Activity (count)")+
  ylim(0, 100)+ 
  theme_bw()+
  theme(legend.position = "none")+
  scale_colour_manual(name  ="Relative size",
                      values = c("#2e72e8", "#fd9087"))+
  geom_segment(aes(x=1.1, xend=1.9, y=15, yend=15), color = "black") + 
  geom_segment(aes(x=2.3, xend=3.1, y=15, yend=15), color = "black") + 
  annotate("text",
           x = c(1.45, 2.7),
           y = c(17, 18),
           label = c("***", "ns"),
           family = "", fontface = 3, size=4)+
           labs(tag = "A")


#Post Activity
ggplot(post_activity_sums, aes( x = Relatedness, y = Swim, color = Size)) + 
  geom_boxplot()+
  geom_point(position=position_jitterdodge(), alpha = 0.3)+
  ylab("Experimental Swimming Activity (count)")+
  ylim(0, 100)+ 
  theme_bw()+
  theme(legend.position = "none")+
  scale_colour_manual(name  ="Relative size",
                      values = c("#2e72e8", "#fd9087"))+
  annotate("text", x = c("Sibs", "Halfsibs", "Nonsibs"), 
           y = 75, label = "* * *") + 
  labs(tag = "B")

```
```{r}
#Post Activity

ggplot(post_activity_sums, 
          aes( x = Relatedness, y = Swim, color = Size))+ 
  geom_boxplot()+
  geom_point(position=position_jitterdodge(), alpha = 0.3)+
  ylab("Experimental Swimming Activity (count)")+
  ylim(0, 100)+ 
  theme_bw()

ggplot(post_activity_sums, 
          aes( x = Relatedness, y = Swim, color = Size))+ 
  geom_boxplot()+
  geom_point(position=position_jitterdodge(), alpha = 0.3)+
  ylab("Experimental Swimming Activity (count)")+
  ylim(0, 100)+
  theme_bw()


```

#MODELLING AND MODEL SELECTION
#PRE ACTIVITY
```{r}
#PRE ACTIVITY SWIMMING----
#nbinom1 = Linear paramaterization
#nbinom2 = Quad. paramerterization
m1<- glmmTMB(Swim ~ Relatedness * Size + (1| Pair_ID) + (1| Family), 
              data = pre_activity_sums, family = "poisson")

m2<- glmmTMB(Swim ~ Relatedness + Size + (1| Pair_ID) + (1| Family), 
                   data = pre_activity_sums, family = "poisson")

m3<- glmmTMB(Swim ~ Relatedness * Size + (1| Pair_ID) + (1| Family), 
                    data = pre_activity_sums, family = nbinom1)

m4<- glmmTMB(Swim ~ Relatedness + Size + (1| Pair_ID) + (1| Family), 
             data = pre_activity_sums, family = nbinom1)

m5<- glmmTMB(Swim ~ Relatedness + Size + (1| Pair_ID) + (1| Family), 
                          data = pre_activity_sums, family = nbinom2)

m6<- glmmTMB(Swim ~ Relatedness * Size + (1| Pair_ID) + (1| Family), 
             data = pre_activity_sums, family = nbinom2)
#AIC PRE----
aic<-AIC(m1, m2, m3,m4, m5, m6)

aic[order(aic$AIC),] 

aic.cand<- list(m1,
                m2, 
                m3, 
                m4, 
                m5, 
                m6)

Cand.names <- c( "m1","m2", 
                 "m3", "m4", "m5", "m6")

aictab(aic.cand, Cand.names, sort = T)

```
Looks like M4 is the big winner here. Let's look more into it.

```{r}
#Summary----
#Always take the interaction
summary(m4) #halfsibs diff from nonsibs

#Dharma Residual Analysis
testDispersion(m4)
simulationOutput <- simulateResiduals(fittedModel = m4, plot = T)

#how about sibs? Must relevel.
pre_activity_sums$Relatedness_Half<- factor(pre_activity_sums$Relatedness, levels = c("Halfsibs", "Sibs","Nonsibs"))
levels(pre_activity_sums$Relatedness_Half)
###
m4a<- glmmTMB(Swim ~ Relatedness_Half + Size + (1| Pair_ID) + (1| Family), 
             data = pre_activity_sums, family = nbinom1)

tab_model(m4,
          transform = NULL,
          show.stat = T,
          show.obs = F, 
          show.r2 = F, 
          show.ngroups = F ,
          show.icc = F,
          show.zeroinf = F,
          string.stat = "z",
          string.est = "Estimate",
          pred.labels = c("(Intercept)", "Siblings",
                          "Nonsiblings",
                          "Size (Large)"),
          dv.labels = "Post-acclimation Activity")

get_variance(m4)

```

#MODEL SELECTION
#POST ACTIVITY
Remember here, there are different trial lengths (3 of 45 ended early due to aggrression levels) so we have to take that into account.
```{r}
###############################################
#POST ACTIVITY-
#DON'T FORGET OFFSET.'

m7<- glmmTMB(Swim ~ Relatedness * Size + (1| Pair_ID) + (1| Family) + offset(log(Duration)), 
             data = post_activity_sums, family = "poisson")

m8<- glmmTMB(Swim ~ Relatedness + Size + (1| Pair_ID) + (1| Family) + offset(log(Duration)), 
             data = post_activity_sums, family = "poisson")

m9<- glmmTMB(Swim ~ Relatedness * Size + (1| Pair_ID) + (1| Family) + offset(log(Duration)), 
             data = post_activity_sums, family = nbinom1, zi = ~1)

m10<- glmmTMB(Swim ~ Relatedness + Size + (1| Pair_ID) + (1| Family) + offset(log(Duration)), 
               data = post_activity_sums, family = nbinom1, zi = ~1)


m11<- glmmTMB(Swim ~ Relatedness + Size + (1| Pair_ID) + (1| Family) + offset(log(Duration)), 
             data = post_activity_sums, family = nbinom2, zi = ~1)

m12<- glmmTMB(Swim ~ Relatedness * Size + (1| Pair_ID) + (1| Family) + offset(log(Duration)), 
             data = post_activity_sums, family = nbinom2, zi = ~1)


#AIC MODEL SELECTION----
aic<-AIC(m7, m8, m9, m10, m11, m12)

aic[order(aic$AIC),] 

#AIC SUMMARY TABLE----
aic.cand<- list(m7, m8, m9, m10, m11, m12)

Cand.names <- c("m7", "m8", "m9", "m10", "m11", "m12")


aictab(aic.cand, Cand.names, sort = T)
```

Looks like m10 is the big winner here. Let's look more into it.

```{r}
#Summary----
summary(m10)
testDispersion(m10)
simulationOutput <- simulateResiduals(fittedModel = m10, plot = T)
#So we have a small issue iwth quantile deviations here. Let's see
#what we can do.
#This issue seems to have resolved when I take into account dispersion of Size
m10a<- glmmTMB(Swim ~ Relatedness + Size + (1| Pair_ID) + (1| Family) + offset(log(Duration)), 
               data = post_activity_sums, family = nbinom1, dispformula = ~ Size)

testDispersion(m10a)
simulationOutput <- simulateResiduals(fittedModel = m10a, plot = T) #Yay! No more issues.

res <- simulateResiduals(m10a, plot = T)
par(mfrow = c(1,3))
plotResiduals(res, post_activity_sums$Relatedness)
testDispersion(res) #model not underdispersed


#TAB MODEL----
tab_model(m10a,
          show.stat = T,
          show.obs = F, 
          show.r2 = F, 
          show.re.var = T,
          show.ngroups = F ,
          show.icc = F,
          show.zeroinf = F,
          string.stat = "z",
          string.est = "Estimate",
          pred.labels = c("(Intercept)", "Halfsiblings", "Siblings",
                          "Size (Large)"),
          dv.labels = "Experimental Activity")

get_variance(m10a) #used for table output because of glmmTMB corrections

```






