---
title: "Aggression and Latency Code"
date: "8/26/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
First, let's load some packages!

```{r}
#First, let's load some packages
library(ggplot2)
library(glmmTMB)
library(tidyr)
library(dplyr)
library(survival)
library(coxme) #cox mixed effect models
library(survminer)
library(AICcmodavg)

#for kind of cool output tables
library(sjPlot)

##optimizers
library(DHARMa)
```

Nice. Next, let's load up that code.
#LOAD IN THE DATA
```{r}
agg<- read.csv("aggression_data_20.csv", header = T)

table((agg$Relatedness))#good, looks like everyone is here! 30 tadpoles per treatment, meaning 15 trials (because of tadpoles were in pairs)

```
Now let's clean up that data. Make it nice and tidy (ha!)
#AGGRESSION TIDY DATA
```{r}
agg<- agg %>% 
  group_by(Pair_ID, Relatedness) %>%
  mutate(mass_diff = max(Mass)- min(Mass),
         totalagg = (Bite_Num)+ (Chase_Num)) #this takes difference in weight between the pair, but keep it positive for each individual 

 ## Adding total aggressive behaviors for each individual tadpole
agg$BiteYN<- ifelse(agg$Bite== "Yes", 1, 0) 

##Let's compare different degrees of relatedness to Non-Sibs
levels(agg$Relatedness)
agg$Relatedness<- relevel(agg$Relatedness, "Nonsibs")
levels(agg$Relatedness)

##Let's make small our intercept here.
levels(agg$Size)
agg$Size<- relevel(agg$Size, "Small")
levels(agg$Size)
```

Great! Well, let's just jump into some plotting, shall we? This plot is to visualize aggression in response to size/mass difference.

#AGGRESSION GRAPH
```{r}
############### ULTIMATE = Relative size diff, experimental mass diff. agg.
#Lutz----
lutz<- ggplot(agg, aes(x = mass_diff, y = totalagg, color= Size))+ 
  geom_point(size = 3.5, alpha = 0.5)+
  facet_wrap(~ Relatedness)+
  stat_smooth(method = "glm", 
              formula = y ~ log(x), 
              fullrange = F ,
              se = F)+
  xlab("Mass difference between tadpoles (g)")+
  ylab("Number of aggressive behaviors by tadpole (count)")+
  theme_bw()+
  theme(legend.position = "top",
        strip.background = element_rect(
          color="black", fill="white", size=0.5, linetype="solid"))

lutz + 
  scale_colour_manual(name  ="Relative size",
                      values = c("#2e72e8", "#fd9087"))+
  guides(size = FALSE)

```
Cute. I love that plot. I think it really does a good job at. . . being a plot.

Well, now let's think about out latency to aggression. Again, back to tidying the ol' data.
#LATENCY TIDY DATA
```{r}
###############  Time-to- Graphical Exploration ########################
###############################################################################

#The code below subsets both the mass difference, aggression difference, and 
#the fastest bite time exhibited between both tadpoles. 

chloe<- 
  agg %>% 
  group_by(Pair_ID, Relatedness) %>%
  summarise( mass_diff = max(Mass)- min(Mass), 
             min_bite_time = min(X1_Bite_Seconds, na.rm = T),#this takes the fastest bite time
             bite_diff = first(Bite_Num) - last(Bite_Num), 
             #this takes the difference between bites 
             #by large and small tadpoles, using large tadpoles as the focal individual
             agg_diff = first(totalagg) - last(totalagg)
  )

#The family value here is that of the first biter
chloe2 <- agg %>% 
  select(Pair_ID, Relatedness, Size, X1_Bite_Seconds, BiteYN, Family) %>%
  group_by(Pair_ID, Relatedness) %>%
  filter(X1_Bite_Seconds == min(X1_Bite_Seconds, na.rm = T)) %>%
  rename(First_Biter = Size) %>%
  select(- X1_Bite_Seconds)


chloe3 <- full_join(chloe, chloe2, by = c("Pair_ID", "Relatedness"))

#here we assign trials where no biting occured (Inf) with 3600, which is 60 minutes.
chloe3$noinf<-ifelse(chloe3$min_bite_time == "Inf", 3600, chloe3$min_bite_time)
chloe3$Relatedness<-relevel(chloe3$Relatedness, "Nonsibs")
chloe3$BiteYN<-tidyr::replace_na(chloe3$BiteYN, 0)

```

Great, so now let's make our super cool time-to-first bite graph!
#LATENCY GRAPH
```{r}

#Here we keep NAs which are labeled in grey. So far my favorite.
time1<-ggplot(chloe3, aes(x = mass_diff, y = noinf/60))+
  geom_point(aes(color = First_Biter), alpha = 0.8, size = 4)+
  facet_wrap(~ Relatedness)+
  ylab("Latency to First Bite in Pair (minutes)")+
  xlab("Difference in size (g)")+
  ylim(0,60)+
  stat_smooth(method="glm",
              formula=y~log(x), 
              se = F, 
              fullrange = T, 
              color = "black", 
              linetype = "F1")+
  theme_bw()+
  theme(legend.position = "top",
        strip.background = element_rect(
          color="black", fill="white", size=0.5, linetype="solid"))

time1 + 
  scale_colour_manual(values = c("#2e72e8", "#fd9087"),
                        na.value = "grey",
                        name  ="First aggressor")
```

Sweetness. Now let's get our modelling on.
#AGGRESSION MODELLING

```{r}
#MASS DIFFERENCE----
#nbinom1 = Linear paramaterization
#nbinom2 = Quad. paramerterization
m1<- glmmTMB(totalagg ~ Relatedness + mass_diff +(1| Pair_ID) + (1| Family)+ offset(log(Duration)),
                         data = agg, family = "poisson")

m2<- glmmTMB(totalagg ~ Relatedness * mass_diff + (1| Pair_ID) + (1| Family)+ offset(log(Duration)), 
           data = agg, family = "poisson")

m3<- glmmTMB(totalagg ~ Relatedness * mass_diff + (1| Pair_ID) + (1| Family)+ offset(log(Duration)), 
                            data = agg, family = nbinom1)

m4<- glmmTMB(totalagg ~ Relatedness * mass_diff + (1| Pair_ID) + (1| Family)+ offset(log(Duration)), 
             data = agg, family = nbinom2)


#Size Categorical----

m5<- glmmTMB(totalagg ~ Relatedness + Size +(1| Pair_ID) + (1| Family)+ offset(log(Duration)),
             data = agg, family = "poisson")

m6<- glmmTMB(totalagg ~ Relatedness * Size+ (1| Pair_ID) + (1| Family)+ offset(log(Duration)), 
             data = agg, family = "poisson")

m7<- glmmTMB(totalagg ~ Relatedness * Size + (1| Pair_ID) + (1| Family)+ offset(log(Duration)), 
             data = agg, family = nbinom1)

m8<- glmmTMB(totalagg ~ Relatedness * Size + (1| Pair_ID) + (1| Family)+ offset(log(Duration)), 
             data = agg, family = nbinom2)


#AIC MODEL SELECTION----
aic<-AIC(m1,
         m2, 
         m3, 
         m4, 
         m5, 
         m6, 
         m7, 
         m8
         ) 
aic[order(aic$AIC),] 

#AIC SUMMARY TABLE----
aic.cand<- list(m1,
                 m2, 
                 m3, 
                 m4, 
                 m5, 
                 m6, 
                 m7, 
                 m8)

Cand.names <- c( "m1","m2", 
                 "m3", "m4", 
                 "m5", "m6", 
                 "m7", "m8")


aictab(aic.cand, Cand.names, sort = T)

#Summary----
summary(m7)
#Dharma Residual Analysis
testDispersion(m7)

#Residual diagnostics are good.

res <- simulateResiduals(m7, plot = T)
par(mfrow = c(1,3))
plotResiduals(res, agg$Relatedness)
testDispersion(res) #model not underdispersed
testZeroInflation(res) #model not zero inflated

#TAB MODEL----
tab_model(m7,transform = NULL,
          show.stat = T,
          show.obs = F, 
          show.r2 = F, 
          show.ngroups = F ,
          show.icc = F,
          string.stat = "z",
          string.est = "Estimate",
          pred.labels = c("(Intercept)", "Halfsiblings", "Siblings",
                          "Size (Large)", "Halfsiblings: Size (Large)", 
                          "Siblings: Size (Large)"),
          dv.labels = "Total aggression")

library(insight)
get_variance(m7)

```
So m7 is our magic number. Let's do a little model deep dive, to see what these numbers really mean.

```{r}
summary(m7)

alpha<- coef(summary(m7))$cond['(Intercept)', "Estimate"] #small nonsibs
betalarge<- coef(summary(m7))$cond['SizeLarge', "Estimate"]
betasibs<- coef(summary(m7))$cond['RelatednessSibs', "Estimate"]
betasibslarge<- coef(summary(m7))$cond['RelatednessSibs:SizeLarge', "Estimate"]
betahalflarge<-coef(summary(m7))$cond['RelatednessHalfsibs:SizeLarge', "Estimate"]
betahalf<- coef(summary(m7))$cond['RelatednessHalfsibs', "Estimate"]

#Small nonsiblings
exp(alpha)

nonsibscat<- exp(alpha)*exp(betalarge) #Large nonsiblings
nonsibscat #0.00148

largesibscat<- exp(alpha)*exp(betasibs)*exp(betalarge)*exp(betasibslarge)
largesibscat #0.0009499

nonsibscat/largesibscat #large nonsibs bite twice as much as large sibs

```


#TIME TO MODEL DESIGN
With time-to data using cox models are without question the most fit to address the data, so let's just go work with that!°

```{r}
#because subsetted data, does Pair_ID disappear
coxmix1<- coxme(Surv(noinf, BiteYN) ~ Relatedness * mass_diff
               + (1 |Family), data = chloe3)
summary(coxmix1)

tab_model(coxmix1,
          transform = NULL,
          show.stat = T,
          show.obs = F,
          show.ngroups = F,
          string.stat = "z",
          string.est = "Estimate",
          pred.labels = c("Halfsiblings", 
                          "Siblings",
                          "Mass_Diff", 
                          "Halfsiblings: Mass_Diff", 
                          "Siblings: Mass_Diff"),
          dv.labels = "Latency to first bite")

```

